% !TeX root = ../report.tex

\begin{abstract}
    The purpose of this Usability Report is to analyze the results of the usability evaluation of the website ``https://www.yesmilano.it/en'' through two different methods: \emph{inspection} (performed by the group members) and \emph{user testing} (performed by a third party voluntaries belonging to a specific user profile).

    For the inspection, we listed the main functionalities of the website and propose several tasks around them. For each task, we analyzed the website according to Nielsen's and MiLe heuristics, assigning scores and documenting with screenshots the website issues.
    
    For the user testing, we collected data directly from 20 possible final users among two different user profiles (students and tourists). Inspectors asked each user to perform a series of tasks. During the process, the inspector monitored and collected data, following quantitative and qualitative indicators. The collected information is then organized in tables and charts.
    
    The results of the two different methodologies were then combined and final conclusions about the usability properties of the website are explained, furthermore providing some potential fixes and improvements to enhance the user experience while browsing the website.
\end{abstract}

\vspace*{5em}
\section*{Disclaimer}

Since the analyzed website presents many sections, we selected a subset of those; in particular, we analyzed pages belonging to:
\begin{itemize}
    \item Guide to the City
    \item Study
    \item Events
    \item Traveller Information
    \item YesMilano Hotels
    \item YesMilano Restaurants
\end{itemize}

On the other hand, we decided to not consider the following sections:
\begin{itemize}
    \item Invest \& Start up
    \item Convetion Bureau
\end{itemize}